Planetary perturbers: Flaring star-planet interactions in Kepler and TESS

### 2023-11-02 src/tex/ms.tex
[showyourwork] overleaf sync
final table upload to zenodo after acceptance

\section*{Acknowledgements}
The authors thank the anonymous referee for their thorough criticism of the manuscript, and numerous valuable suggestions. EI would like to thank Antonino Lanza for helpful advice.
This paper includes data collected by the TESS mission, which are publicly available from the Mikulski Archive for Space Telescopes (MAST).
Funding for the TESS mission is provided by NASA’s Science Mission directorate. 
This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
KP, JC and NI acknowledge funding from the German \textit{Leibniz Community} under grant P67/2018.
%follow instructions here https://gea.esac.esa.int/archive/documentation/GEDR3/Miscellaneous/sec_credit_and_citation_instructions/
\section*{Data Availability}
All data used in this study are publicly available in their respective archives.
This study used the reproducibility software \href{https://github.com/showyourwork/showyourwork}{showyourwork}
\citep{luger2021mappinga} to create all figures, format all tables, and compile the manuscript. Each figure links to the dataset stored on Zenodo (link to be added after acceptance), and to the script that produced the figure in the git repository~\href{https://github.com/ekaterinailin/flaring-spi-paper}{github.com/ekaterinailin/flaring-spi-paper}. The git repository that produces the data stored on Zenodo is publicly available at \href{https://github.com/ekaterinailin/flaring-spi}{github.com/ekaterinailin/flaring-spi}. 
\bibliography{bib}

>>>>

\section*{Acknowledgements}
The authors thank the anonymous referee for their thorough criticism of the manuscript, and numerous valuable suggestions. EI would like to thank Antonino Lanza for helpful advice.
This paper includes data collected by the TESS mission, which are publicly available from the Mikulski Archive for Space Telescopes (MAST).
Funding for the TESS mission is provided by NASA’s Science Mission directorate. 
This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
KP, JC and NI acknowledge funding from the German \textit{Leibniz Community} under grant P67/2018.
%follow instructions here https://gea.esac.esa.int/archive/documentation/GEDR3/Miscellaneous/sec_credit_and_citation_instructions/
\section*{Data Availability}
All data used in this study are publicly available in their respective archives.
This study used the reproducibility software \href{https://github.com/showyourwork/showyourwork}{showyourwork}
\citep{luger2021mappinga} to create all figures, format all tables, and compile the manuscript. Each figure links to the script that produced the figure in the git repository~\href{https://github.com/ekaterinailin/flaring-spi-paper}{github.com/ekaterinailin/flaring-spi-paper}. The git repository that produces the data stored on Zenodo is publicly available at \href{https://github.com/ekaterinailin/flaring-spi}{github.com/ekaterinailin/flaring-spi}. The almost 13000 de-trended light curves, and the full versions of all Tables in this work are available via Zenodo \href{https://doi.org/10.5281/zenodo.8355002}{10.5281/zenodo.8355002}.
\bibliography{bib}
